\bf Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-14 notes/notes.tex
obtained Gzz and pole positions of Gzz in metal and lm

@@

%\clearpage
\section{Evidence for the Mott MIT}
Through the URG study of the generalised SIAM with correlation (eq.~\ref{siam_attr}) shown in chapter \ref{siam-attr-chap}, we can conclude the following about that model:
\begin{itemize}
	\item For \(U_b > J/4\), the couplings \(J\) and \(V\) become irrelevant while \(U\) is relevant, which means that \textbf{the impurity gets cut off from the bath at low energies}.
\begin{center}
	\includegraphics[width=0.7\textwidth]{../figures/phase-map_D=1000.pdf}
\end{center}
	\item Study of the impurity spectral function shows a gap at low \(\omega\) for \(U_b > J/4\). Other measures like mutual information and spin-spin correlations also show a sharp change on crossing that value, demonstrating \textbf{the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity}.
\begin{center}
	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.000.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.40.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/corr-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r1p-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
\end{center}
	\item In the context of the auxiliary model, this represents an \textbf{impurity phase transition} from the completely-screened spin-singlet phase to the unscrened local moment phase.
\begin{center}
	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=4.000.pdf}
\end{center}

>>>>

\subsection{Bath spectral function \(A_{00}(\omega)\)}
\begin{center}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_U_by_J=0.040.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_U_by_J=0.141.pdf}\\
	\includegraphics[width=0.48\textwidth]{../figures/spec_func_00_U_by_J=0.185.pdf}
	\includegraphics[width=0.48\textwidth]{../figures/spec_func_00_U_by_J=0.250.pdf}\\
\end{center}

\subsection{Position of lowest-energy pole}
\begin{center}
	\includegraphics[width=0.48\textwidth]{../figures/poles_lm.pdf}
\end{center}

@@

%\clearpage
\section{Evidence for the Mott MIT}
Through the URG study of the generalised SIAM with correlation (eq.~\ref{siam_attr}) shown in chapter \ref{siam-attr-chap}, we can conclude the following about that model:
\begin{itemize}
	\item For \(U_b > J/4\), the couplings \(J\) and \(V\) become irrelevant while \(U\) is relevant, which means that \textbf{the impurity gets cut off from the bath at low energies}.
\begin{center}
	\includegraphics[width=0.7\textwidth]{../figures/phase-map_D=1000.pdf}
\end{center}
	\item Study of the impurity spectral function shows a gap at low \(\omega\) for \(U_b > J/4\). Other measures like mutual information and spin-spin correlations also show a sharp change on crossing that value, demonstrating \textbf{the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity}.
\begin{center}
	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.040.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.26.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.040.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.250.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.26.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/corr-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r1p-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
\end{center}
	\item In the context of the auxiliary model, this represents an \textbf{impurity phase transition} from the completely-screened spin-singlet phase to the unscrened local moment phase.
\begin{center}
	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=4.000.pdf}
\end{center}
